---
title: "Marketing Analytics Report"
subtitle: "Project-3_Office"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, comment = NA, message = F, warning = F, fig.align = "center")
options(pillar.sigfig = 7)
options(scipen = 999)
```

```{r}
library(magrittr ) 
library(tidyverse)
library(flexclust)
```
<font size="2"> Load the libraries</font>

# Question-1) 

```{r} 
office<- read.csv("office.csv")
summary(office)
glimpse(office)
```

<font size="2">This databse contains data of the 200 respondents and their choice of preferences when it comes to buy the office is equipment</font>

  
# Question-2) 


```{r}

office_normalized<- scale(office[, c(
                           "variety_of_choice",
                           "electronics",
                           "furniture",
                           "quality_of_service",
                           "low_prices",
                           "return_policy"
                           )]) %>% 
  as_tibble() 

```


```{r}
summary(office_normalized)
```
<font size="2"> Mean of the normalized attributes is zero always</font>
<font size="2"> Electronics attribute has the maximum and minimum value </font>


# Question-3) 


```{r}

distances <- dist(office_normalized, 
                  method = "euclidean")

as.matrix(distances)[1:5, 1:5] 
```


```{r}
hier_clust <- hclust(distances, method = "ward.D2") 
```

<font size="2">plot the dendogram of the hierarchical clustering process</font>
```{r}
plot(hier_clust)
```


# Question-4) 
```{r}

plot(hier_clust)
rect.hclust(hier_clust, k = 6, border = "skyblue")
hiercut_obs <- cutree(hier_clust, k = 6)
table(hiercut_obs)

```


# Question-5) 


```{r}
office_normalized %>%
  mutate(hiercut_obs = factor(hiercut_obs)) %>%
  group_by(hiercut_obs) %>% 
  mutate(n=n())%>%
  summarise_all(~mean(.x)) %>%  
  mutate(prop=n/sum(n))%>%
  print(width = Inf) 

options("install.lock"=FALSE)

h_flexclust <- as.kcca(hier_clust, office_normalized, k = 6)

table(hiercut_obs, clusters(h_flexclust))
```

```{r}
barchart(h_flexclust, main = "Segment Profiles")
```
# Question-6) 

From the table output, 


# Question-7) Comment on why you may decide to NOT proceed with this 6-cluster solution.


# Question-8) Generate a 5-cluster solution. How many observations are assigned to each cluster?

```{r} 
hier_clust_5 <- hclust(distances, method = "ward.D2")
plot(hier_clust_5)
rect.hclust(hier_clust_5, k = 5, border = "skyblue")
hier_clust_obs_5 <- cutree(hier_clust_5, k = 5)
table(hier_clust_obs_5)

```


# Question-9) 
```{r}

```


```{r}
options("install.lock"=FALSE)

office_normalized %>%
  mutate(hier_clust_obs_5 = hier_clust_obs_5) %>%
  group_by(hier_clust_obs_5) %>% 
  mutate(n=n())%>%
  mutate(prop=n/sum(n))%>%
  summarise_all(~mean(.x)) %>% 
  print(width = Inf) 

hier_flex_5 <- as.kcca(hier_clust_5, office_normalized, k = 5)
table(hier_clust_obs_5, clusters(hier_flex_5))

barchart(hier_flex_5, main = "Segment Profiles")


hier_clust_obs_5 <- factor(hier_clust_obs_5,
              levels = c(1, 2, 3, 4, 5),
              labels = c("quality_of_service Hierachy", "electronics Hierachy", "furniture Hierachy",
                         "Professional_service Hierachy",
                         "Non-Professional_service Hierachy"))

```







# Question-10)


----

# Question-12) 


```{r}

set.seed(123) 

kmeans <- kmeans(office_normalized, 
                       centers = 5, 
                       iter.max = 1000,
                       nstart = 100)


kmeans_labels <- factor(
  kmeans$cluster,
  levels = c(1, 2, 3, 4, 5),
  labels = c("quality_of_service K-means", "electronics K-means", "furniture K-means",
             "Professional_service K-means",
             "Non-Professional_service K-means"))

table(kmeans$cluster)
```


# Question-13) 

```{r}
table(kmeans$cluster, hier_clust_obs_5)
```


```{r}
hitrate <- (59+60+17+33+29)*100
hitrate <- hitrate / 200
hitrate
```


