---
title: "Project-2"
date: "23/05/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



#required libraries
```{r}

#install.packages("tidyverse")
#install.packages("broom")
#install.packages("pROC")
#install.packages("dplyr")
#install.packages("forestmangr")
#install.packages("ggplot2")
#install.packages("ggmosaic")
#install.packages("ggpubr")
```


#Load the libraries 

```{r}
library(tidyverse)
library(forestmangr)
library(broom)
library(dplyr)
library(pROC)
library(ggplot2)
library(ggmosaic)
library(ggpubr)
```

## 1st question

#Import the dataset ecommerce

```{r}
browsing <- read.csv("C:\\Users\\vt00196\\OneDrive - University of Surrey\\Desktop\\Marketing Analytics\\project 2\\ecommerce.csv")
```

# Summary and glimpse

```{r}
summary(browsing)
```



##2nd question

# Before model buidling convert the output and input variables into factors as it is categorical form
```{r}
browsing$discount <- as.factor(browsing$discount)
browsing$source <- as.factor(browsing$source)
browsing$conversion <- as.factor(browsing$conversion)
```


```{r}
m1 <- glm(conversion ~ discount, data = browsing, family = "binomial")

summary(m1)
```



##3rd question
```{r}
exp(coef(m1))
```


## 4th question
```{r}
exp(confint(m1))
```



## 5th question

```{r}
ggplot(data = browsing) + 
  geom_mosaic(aes( 
    x = product(discount),  
    fill = conversion), 
    offset = 0.02,  
    divider = ddecker()) + 
  facet_grid(~source,
             scales = "free") + 
  theme_pubr() + 
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(angle = 90)) + 
  labs(x = "", y = "") 
```


# The conversion through source direct and search is higher when discount is given

## 6th question

# Considering discount and source as variables input to the model 2
```{r}
m2 <- glm(conversion ~ discount + source, data = browsing, family = binomial)
summary(m2)
```
# Both the variables are statistically significant and both of them have positive co-efficients 

## 7th question

```{r}
exp(coef(m2))
```



## 8th question

# Model-3 with discount and source and including their interaction

```{r}
m3 <- glm(conversion~source + discount + discount:source, data = browsing, family = binomial)
```

```{r}
summary(m3)
```


## 9th question
```{r}
exp(coef(m3))
exp(confint(m3))
```


## 10th question

# Including all the variables and interaction of discount and source for model-4
```{r}
browsing$country <- as.factor(browsing$country)
```


```{r}
m4 <- glm(conversion ~ discount + source + visit_duration + total_pages_visited + country + discount:source, data = browsing, family = binomial)
```


```{r}
summary(m4)
```

## 11th question

```{r}
cor.test(browsing$total_pages_visited, browsing$visit_duration)
```


## 12th question

# Model-5  
```{r}
m5 <- glm(conversion ~ discount + source + total_pages_visited + country + discount:source, data = browsing,  family = binomial)
```
```{r}
summary(m5)
```



## 13th question

```{r}
tidy(m5) %>% # tidy function from broom package
  mutate(exp_beta_llci = exp(confint(m5))[, 1], # lower ci
         exp_beta = exp(estimate), # odds ratio, midpoint
         exp_beta_ulci = exp(confint(m5))[, 2]) %>% # upper 
  select(term, estimate, exp_beta_llci, exp_beta, exp_beta_ulci) %>% 
  ggplot(aes(x = term, 
             y = exp_beta,
             ymin = exp_beta_llci,
             ymax = exp_beta_ulci)) +
  geom_point(size = 4) + 
  geom_errorbar(width = 0.25) +
  # add a horizontal line where odds ratio == 1.0 (no effect):
  geom_hline(yintercept = 1, linetype = "dashed", 
                    size = 1, color = "dodgerblue") + 
  labs(title = "95% CI: Pass sign up odds by factor",
       x = NULL,
       y = "Likehood by Factor (odds ratio, main effect)") + 
  coord_flip() + # rotates the plot
  theme_pubr()

```


## 14th question

```{r}
browsing$base_probability <- predict(
  m5,
  browsing,
  type = "response"
)

head(browsing)
```


```{r}
mean(browsing$base_probability)
```

# The mean value of the base probability is 0.1759163

## 15th question

```{r}
browsing$pred_conversion <- 1 * (browsing$base_probability >= 0.5)

head(browsing)
```


```{r}
table(browsing$conversion, browsing$pred_conversion)
```

# The true positives are 908 and the people getting converted into conversion is 908 and not getting converted is 20,190

## 16th question

```{r}
#Accuracy
(20190+908)/(20190+450+908+3498)
```

## 17th question

```{r}
rocobj <- roc(browsing$conversion, # actual reference
              browsing$base_probability) # predictions 

# area under the curve
rocobj$auc

# plot the ROC curve
ggroc(rocobj, 
      color = "dodgerblue", 
      size = 1,
      legacy.axes = T) + # the specificity axis (x axis) plotted as increasing “1 - specificity”
  geom_segment(x = 0, y = 0, xend = 1, yend = 1, linetype = 2, alpha  =  0.01) + # plot the diagonal line
  theme_pubr() +
  labs(title = sprintf("ROC Curve (AUC = %.5f)", rocobj$auc), # plot the auc as title
       x = "1 - Specificity (or fpr)", 
       y = "Sensitivity (or tpr)")
```


The area under the curve is 77.49%

## 18th question

```{r}
browsing_new <- browsing
browsing_new$total_pages_visited <- browsing_new$total_pages_visited+1

browsing_new$new_prob <- predict(m5, browsing_new, type = "response")
```


```{r}
mean(browsing_new$new_prob)
mean(browsing_new$base_probability)
```


## 19th question

```{r}
(mean(browsing_new$new_prob) - mean(browsing_new$base_probability))/mean(browsing_new$base_probability)
```















