---
title: "Marketing Analytics Report"
subtitle: "Project 3"
output:
  html_document:
    self-contained : yes
    fig_caption: yes
    highlight: pygments
    theme: flatly
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: no
      smooth_scroll: yes
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = T, comment = NA, message = F, warning = F, fig.align = "center")
options(pillar.sigfig = 7)
options(scipen = 999)
```

## 1st question

Read and inspect the data set. Provide a descriptive analysis for each of the variables in the data set. Make sure you provide an analysis that is meaningful for each variable type (e.g., factors, identifiers).

### Preamble

----

### Libraries

In this session we will use the following r packages. Make sure these packages are installed (by using the `installl.paclages` function) on your device before you begin.

```{r}
library(tidyverse) # for data wrangling and viz
library(ggpubr) # for theme_pubr
library(dfidx) # for indexed data frames
library(mlogit) # multinomial logit
library(broom) # for tidy model output
```

----

### Data

Let's first read the data set onto our R session.

```{r}
# read in the data
virtual_storage <- read.csv("cloud.csv",stringsAsFactors=T)

```

Let's inspect the data using the `glimpse` function.

```{r}
glimpse(virtual_storage)
```

### Descriptives

```{r}
summary(virtual_storage)
```


```{r}
table(virtual_storage$cloud_storage)
table(virtual_storage$cloud_services)
table(virtual_storage$price)
```


## 2nd question

Convert the attribute variables cloud_storage and price. Why there is no need to perform this step on the rest of the attribute variables?

```{r}
virtual_storage$cloud_storage <- relevel(virtual_storage$cloud_storage, ref = '30gb')
virtual_storage$price <- relevel(virtual_storage$price, ref = 'p6')
```

## 3rd question 

Create a new variable in the data set that turns price into numeric class. Call this new variable price_n. What is the mean of variable price_n?

```{r}
virtual_storage['price_n']<- virtual_storage$price
virtual_storage<- virtual_storage %>% 
  mutate(price_n = gsub("p", "", price_n), # remove character 'p' from
         price_n = as.numeric(price_n)) # turn the variable into numeric class

```


```{r}
head(virtual_storage)
```

```{r}
#mean of price_n
mean(virtual_storage$price_n)
```

## 4th question

 how many times did respondents choose a 30GB cloud storage? 
 What is the percentage of respondents who chose email only as cloud service?

```{r}
vs1<- virtual_storage %>% group_by(cloud_storage, choice) %>% summarise(n = n()) %>% ungroup() %>% arrange(desc(n))
print(vs1)
```

```{r}
vs2<- virtual_storage %>% group_by(cloud_services, choice) %>% summarise(n = n()) %>% ungroup() %>% arrange(desc(n))
print(vs2)
```


```{r}
vs3<- virtual_storage %>% group_by(cloud_storage, cloud_services, choice) %>% summarise(n = n()) %>% ungroup() %>% arrange(desc(n))
print(vs3)
```


## 5th question


```{r}
#Shape data for mlogit
m_data <- dfidx(virtual_storage, # the data set to use
                choice = "choice", # variable that contains choice
                idx = list(c("choice_id", "respondent_id"), #the two indexes(choice set & respondent) that define unique obs 
                           "alternative_id")) # the levels of the alternatives
# print
m_data 
```

## 6th question
Use m_data to build a multinomial logit model that predicts choice from cloud_storage, customer_support, cloud_services, and price.
Comment on the coefficient estimates of cloud_storage5000gb and pricep12.
```{r}
# for reproducibility
set.seed(123) 

# estimate the model
model1 <- mlogit(choice ~ 0 + cloud_storage + customer_support + cloud_services + price, data = m_data)

# print the model output
summary(model1)$CoefTable 
```
 
 
## 7th question
 build a multinomial logit model that uses price_n instead of price.
 Comment on the coefficient estimate of price_n.

```{r}
# for reproducibility
set.seed(123) 

# estimate the model
model2 <- mlogit(choice ~ 0 + cloud_storage + customer_support + cloud_services + price_n, data = m_data)

# print the model output
summary(model2)$CoefTable 
```
 
 
 
## 8th question
Use a likelihood ratio test to test the model2 against model1.
 
```{r}
#likelihood-ratio test
lrtest(model1,model2)
```
. 

## 9th question
Use model2 to predict the choice probabilities for different alternatives in the data. What is the predicted probability of choosing the third alternative in the first choice set?
```{r}
head(predict(model2, m_data), 1)
```
The 3rd alternative in first set is 0.02837

```{r}
predicted_propabilities <- predict(model2, m_data) %>% 
  as_tibble()

# print the predictions
predicted_propabilities
```

## 10th question

```{r}
predicted_alternative <-
  predicted_propabilities %>% 
  rowid_to_column("choiseset_id") %>% 
  pivot_longer(!choiseset_id, names_to = "choice", values_to = "prob") %>% 
  group_by(choiseset_id) %>% 
  slice(which.max(prob)) %>% 
  ungroup() %>% 
  select(choice) %>% 
  as_vector()

predicted_alternative
```


## 11th question

```{r}
selected_alternative <- 
  virtual_storage %>% 
  filter(choice > 0) %>% 
  select(alternative_id) %>% 
  as_vector()


selected_alternative
```

In the 15th choice set 2nd alternative is the selected alternative.

## 12th question

```{r}
table(selected_alternative, predicted_alternative)
```
```{r}
# Accuracy or Hit rate 
(579+624+614)/(579+211+197+190+624+200+185+200+614)
```
Accuracy or Hit rate = Diagonal values / All Values = 60.56%

## 13th question

```{r}
# Custom function 
predict.share <- function(model, d) {
  temp <- model.matrix(update(model$formula, 0 ~ .), data = d)[, -1] # generate dummy matrix
  u <- temp %*% model$coef[colnames(temp)] # calculate utilities
  probs <- t(exp(u) / sum(exp(u))) # calculate probabilities
  colnames(probs) <- paste("alternative", colnames(probs))
  return(probs)
}

```

## 14th question
Creating a data object with the following hypothetical market consisting of 5 alternatives.
```{r}
d_base <- virtual_storage[
  c(525, 1043, 3138, 20, 877), # take the 526th, 1044th, 3139rd, 21th & 878th observation from the data set
  c("cloud_storage", "customer_support", "cloud_services", "price_n") # take attribute columns
  ]

# print
d_base
```

## 15th question

```{r}
# run the custom function and attach its output
d_base <- cbind(d_base, as.vector(predict.share(model2, d_base)))

# print
d_base
```

## 16th question

```{r}
# make a copy of the d_base data
d_new <- d_base

# update d_new data so that the value of row 5 and column "cloud service" is now "email,video"
d_new[5, "cloud_services"] <- "email, video"

# re-run the custom function and attach its output
d_new$predicted_share <- as.vector(predict.share(model2, d_new))

# print
d_new

```

## 17th question

Comparison of market shares after the chance in cloud_services

## 18th question
```{r}
# Willingness to pay for customer support 
- coef(model2)["customer_supportyes"] / coef(model2)["price_n"]
```

## 19th question
```{r}
# Willingness to pay Upgrade from 30gb to 2000gb
- coef(model2)["cloud_storage2000gb"] / coef(model2)["price_n"]
```

## 20th question

```{r}
# Willingness to pay Upgrade from 2000gb to 5000gb
- (coef(model2)["cloud_storage5000gb"] - coef(model2)["cloud_storage2000gb"]) / coef(model2)["price_n"]
```




 